---
title: "Stat Dept Instruction History"
author: "Brian S Yandell"
date: "June 26, 2014"
output: beamer_presentation
---

## First we do some data setup.

- Read in CSV file.
- Find enrollment per lecture/discussion.
- Remove non-Stat courses.
- Keep Math 431 handy.
- Pull out lectures only.
- Fix recording problems.
- Organize course by groups.

```{r}
source("query.R")
```

## Then make plots.

- Plot Enrollment per Year by Course Group.

```{}
library(lattice)
lecploty(query, group = course.group)
```

- Plot Enrollment per lecture over years by course.

```{}
lec <- query[query$SECTION.NUMBER < 300 & 
               query$term != "Summer", ]
xyplot(enroll ~ TERM | CATALOG.NUMBER, lec)
```

## Enrollment for Undergrad Courses

```{r, echo=FALSE}
library(lattice)
lecploty(query, (query$CATALOG.NUMBER < 500), course.group, title = "Undergrad Courses")
```

## Instructor for UG Classes

```{r, echo=FALSE}
lecploty(query, query$year != "2014-2015" & query$CATALOG.NUMBER < 600, query$instructor, smooth=FALSE,
         title = "Instructor for Undergrad Classes")
```

## Instructor for Gateway Classes

```{r, echo=FALSE}
lecploty(query, query$year != "2014-2015" & query$CATALOG.NUMBER %in% gateways, query$instructor, smooth=FALSE,
         title = "Instructor for Gateway Classes")
```

## Enrollment for Gateway Classes

```{r, echo=FALSE}
lecploty(query, (query$CATALOG.NUMBER %in% gateways), query$CATALOG.NUMBER, smooth = FALSE,
         title = "Gateway Courses")
```

## Gateway Enrollment per Lecture

```{r, echo=FALSE}
tmp <- query[query$CATALOG.NUMBER %in% gateways & query$SECTION.NUMBER < 300 &
               !(query$CATALOG.NUMBER %in% c(201,302)) & !(query$term == "Summer") &
               !(query$year == "2014-2015"), ]
tmp$course <- ordered(tmp$CATALOG.NUMBER)
xyplot(enroll ~ TERM | course, tmp, type = c("p","smooth"),
       main = "Gateway Enrollments per Lecture")
```

## Math Stat Courses by Year.

```{r, echo=FALSE}
tmp <- rbind(query, math431)
lecploty(tmp, (tmp$CATALOG.NUMBER %in% mathstats), tmp$CATALOG.NUMBER, smooth = FALSE,
         title = "Math-Stat Courses")
```

## Math Stat Courses by Term.

```{r, echo=FALSE}
lecplott(tmp, (tmp$CATALOG.NUMBER %in% mathstats), tmp$CATALOG.NUMBER, smooth = FALSE,
         title = "Math-Stat Courses")
```

## Math-Stat Enrollment per Lecture

```{r, echo=FALSE}
tmp <- tmp[tmp$CATALOG.NUMBER %in% mathstats & tmp$SECTION.NUMBER < 300 & !(tmp$term == "Summer") &
               !(tmp$year == "2014-1015"), ]
tmp$course <- ordered(tmp$CATALOG.NUMBER, c(309,310,431,311,312))
xyplot(enroll ~ TERM | course, tmp, type = c("p","smooth"),
       main = "Math Stat Enrollments per Lecture")
```